
ran on R 4.5.0

```{r message=FALSE, warning=FALSE}
library(Seurat)
library(Matrix)
library(zellkonverter)
library(SummarizedExperiment)
library(SingleCellExperiment)
library(dplyr)
library(ggplot2)
library(ggrastr)
library(patchwork)
```

read in data, convert to Seurat, and clean up 
```{r message=FALSE, warning=FALSE}
adata <- readH5AD("adata_highconf_filtered.h5ad") 
colnames(colData(adata))[colnames(colData(adata)) == "cell_type_high"] <- "cell_type"

#build Seurat object on raw counts 
counts <- assay(adata, "X_raw")
seurat_obj <- CreateSeuratObject(counts = counts, meta.data = as.data.frame(colData(adata)))

#add log-normalized data as a layer called "data"
seurat_obj[["RNA"]] <- SetAssayData(object = seurat_obj[["RNA"]], layer = "data", new.data = assay(adata, "X"))

#add UMAp to Seurat object 
umap_mat <- reducedDim(adata, "X_umap")
colnames(umap_mat) <- c("UMAP_1", "UMAP_2")
identical(colnames(seurat_obj), rownames(umap_mat))

seurat_obj[["umap"]] <- CreateDimReducObject(embeddings = umap_mat, key = "UMAP_", assay = DefaultAssay(seurat_obj))

# Count cells per cell_type
celltype_counts <- seurat_obj@meta.data %>% count(cell_type)

# Cell types with > 1 cell
keep_celltypes <- celltype_counts %>% filter(n > 1) %>% pull(cell_type)

# Subset Seurat object
seurat_filt <- subset(seurat_obj, subset = cell_type %in% keep_celltypes)

#filter for high probability cells 
seurat_filt_highprob <- subset(seurat_filt, subset = cell_type_high_prob > 0.7)
seurat_filt = seurat_filt_highprob
```

look at confidence in existing cell calls 

called (broad) cell type by celltypist 
```{r}
DimPlot(seurat_filt,reduction = "umap",group.by = "cell_type_high")
```
confidence of the broad calls 
```{r}
df <- cbind(Embeddings(seurat_filt, "umap"), seurat_filt@meta.data)
hist(df$cell_type_high_prob, 100)
ggplot(df, aes(UMAP_1, UMAP_2, color = cell_type_high_prob)) + geom_point_rast(size = 0.5) + theme_bw()
```
confidence of the more specific calls 
```{r}
hist(df$cell_type_low_prob, 100)
ggplot(df, aes(UMAP_1, UMAP_2, color = cell_type_low_prob)) + geom_point_rast(size = 0.5) + theme_bw()
```



finding marker genes and most highly expressed genes per cluster 

```{r}
DimPlot(seurat_filt, reduction = "umap", group.by = "leiden", label = TRUE, repel = TRUE)
```
```{r}
seurat_filt2 = seurat_filt
Idents(seurat_filt2) <- "leiden"
```

this code finds genes enriched in a cluster compared to all others (only variable genes)
```{r}
markers_list_all <- FindAllMarkers(seurat_filt2, features = VariableFeatures(seurat_filt2), min.pct = 0.25, logfc.threshold = 0.25)
```
then for each cluster you can go in and look at the top genes to determine cell identity e.g. leiden 5
```{r}
markers_list_all %>% filter(cluster %in% c("5")) %>% dplyr::arrange(desc(avg_log2FC)) %>% head(10)
#top markers for this cluster indicative of NK cells 
c("KLRF1",  "SH2D1B", "SPON2",  "GNLY",   "CLIC3",  "NMUR1",  "KLRC1",  "ERBB2",  "DTHD1",  "GZMB")
```

re-assigning cell type for a leiden 
```{r}
seurat_filt$cell_type_new <- "unassigned"
expr_matrix <- Seurat::GetAssayData(seurat_filt, assay = "RNA", slot = "data")
```

```{r}
genes_of_interest <- c("KLRF1",  "SH2D1B", "SPON2",  "GNLY",   "CLIC3",  "NMUR1",  "KLRC1",  "ERBB2",  "DTHD1",  "GZMB")
avg_expr <- Matrix::colMeans(expr_matrix[genes_of_interest, , drop = FALSE])
hist(avg_expr)
seurat_filt$cell_type_new[seurat_filt$leiden %in% c("5") & avg_expr > 0.5] <- "NK"
```
